A Switching Planner for Combined Task and Observation Planning

### 2011-04-21 subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
few suggestions from moritz
not sure what I changed in related
Hi Moritz, I have merged the material I think we should have added to the paper...

Also leveraging deterministic planners in problems that feature
uncertainty, \system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009} demonstrate how conformant planning
---i.e., sequential planning in unobservable worlds--- can be modelled
as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. Most
recently this research thread has been extended to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.

%% Their applicability in our setting is
%% limited, firstly because they only scale to smaller problems, with
%% thousands of states, and also due to the large amount of
%% \emph{problem-specific} offline processing that might be required to get useful
%% search guidance.

%%  In that
%% setting \citeauthor{kurniawati:etal:2010}~(\citeyear{})
%% recently addressed an inefficiency of offline point-based techniques
%% in problems with medium length planning horizons, however their
%% approach take tens of minutes to good plans, and only scales to tens
%% of thousands of states. In the case of general domain-independent
%% factored systems, the state-of-the-art scales to relatively small
%% problems with $2^{22}$ states~\cite{shani:etal:2008}.

%% At their limit,
%% these procedures take over an hour to converge, and $\sim10$ seconds
%% on average to perform a single Bellman backup.  For classes of POMDP
%% that feature exploitable structures (e.g., no actions with negative
%% effects), problems with as many as $10^{30}$ states can be targeted by
%% such offline procedures~\cite{brunskill:russell:2010}.

%% Although we suppose it an interesting
%% item for future work to pursue that direction, it should be noted that
%% ease of goal reachability is not guaranteed in the problems we face,
%% and is certainly not a property to be assumed in domain independent
%% planning.

%%
%% The continual planning system that motivated our
%% project~\cite{brenner:nebel:jaamas09} also has this characteristic,
%% and has been applied in completely observable domains, particularly
%% those featuring multiple communicating agents.

%% The use of knowledge
%% operators in domains allows plans that act to gain knowledge, but the
%% approach assumes that such actions are deterministic and reliable, an
%% assumption that we relax.

%%No! They simply haven't been evaluated in PO settings. They may, or
%%may not struggle. They have sampling of traces, and that would
%%include observations, and therefore evolutions of beliefs. SSAT was
%%proposed by Littman for POMDPs. So the majercik stuff is perfectly
%%suited to POMDPs.

% Normally if we are going to compare with related work, we do
% actually *compare*. Why didn't you try those approaches? I think
% it's safe to say that FFR will struggle. Why would it even include
% in its plan an observational action that doesn't change the world?

%%
%% However, as we said in the introduction,
%% all these approaches struggle in partially observable domains as they
%% rely on being able to determine the state at all times.

>>>>

Also leveraging deterministic planners in problems that feature
uncertainty, \system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009} demonstrate how conformant planning
-- i.e., sequential planning in unobservable worlds -- can be modelled
as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. We
consider it an appealing future direction to pursue conformant
reasoning during the sequential sessions we proposed. Most recently
this research thread has been extended to contingent planning in fully
observable non-deterministic environments~\cite{albore:etal:2009}.
